Initial Analysis

### 2019-12-31 Initial_Analysis.Rmd
Colors!

Status_Plot_Data %>%
  ggplot() + 
  geom_bar(aes(x=id,
               y=value, 
               fill=observation),
           stat="identity", 
           alpha=0.5) +
  scale_fill_manual("Catch Category",
                    values = c(
                      "#9986A5", # Developing / Rebulding / Cat A / blue
                      "#79402E", #Max exp. / Cat B / green
                      "#CCBA72", # collapsed / Overexp. / Cat. C / Red
                      "#8D8680"
                    ),
                    na.value = "white"
  ) +
  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "black", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "black", alpha=1, size=0.3, inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "black", alpha=1, size=0.3, inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, 
                                   y = -50, 
                                   xend = start, 
                                   yend = -50), colour = "black", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  # Add text showing the value of each 100/75/50/25 lines
  ggplot2::annotate("text", 
                    # x = rep(max(data$id),3),
                    x =c(0,0,0.2,0.2),
                    y = c(-50, 0, 50, 100),
                    label = c("50","0", "50", "100") , 
                    color="black", 
                    size=5, 
                    angle=0, 
                    # fontface="bold",
                    hjust=1) +
  # Add labels on top of each bar
  geom_text(data=label_data,
            aes(
              x = id,
              y = 101,
              label=individual,
              hjust=hjust),
            color="black",
            # fontface="bold",
            alpha=1,
            size=4,
            angle= label_data$angle,
            inherit.aes = FALSE ) +
  # Continents labels
  geom_text(data=base_data,
            aes(x = title,
                y = 85, 
                label=group), 
            hjust=c(1,1,1,0,0,0),
            colour = "black",
            # alpha=0, 
            size=5,
            fontface="bold",
            inherit.aes = FALSE) +
  ylim(-100,105) +
  theme_minimal() +
  theme(legend.position = c(0.93,0.14),
    legend.key.size = unit(1,"cm"),
    legend.title = element_text(size = 16),
    legend.text = element_text(size = 14),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm")) +
  coord_polar()

@@

ggsave(
    plot = last_plot(),
    width = 17,
    height = 15,
    units = "in",
    filename = "Plot.png"
    # filename = "Territory_circular_status.png",
    # path = Figures_Path
  )

>>>>

Status_Plot_Data %>%
  ggplot() + 
  geom_bar(aes(x=id,
               y=value, 
               fill=observation),
           stat="identity", 
           alpha=0.5) +
  # scale_fill_manual("Catch Category",
  #                   values = c(rev(wes_palette(n = 5, name = "Rushmore1")),"grey")
  #                   ) +
  scale_fill_manual("Catch Category",
                    values = c(
                      "#046C9A", # Developing / Rebulding / Cat A / blue
                      "#0B775E", #Max exp. / Cat B / green
                      "#F2300F", # collapsed / Overexp. / Cat. C / Red
                      "#8D8680"
                    ),
                    na.value = "white"
  ) +
  # Add a val=100/75/50/25 lines. I do it at the beginning to make sur barplots are OVER it.
  geom_segment(data=grid_data, aes(x = end, y = 0, xend = start, yend = 0), colour = "black", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 50, xend = start, yend = 50), colour = "black", alpha=1, size=0.3, inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, y = 100, xend = start, yend = 100), colour = "black", alpha=1, size=0.3, inherit.aes = FALSE ) +
  geom_segment(data=grid_data, aes(x = end, 
                                   y = -50, 
                                   xend = start, 
                                   yend = -50), colour = "black", alpha=1, size=0.3 , inherit.aes = FALSE ) +
  # Add text showing the value of each 100/75/50/25 lines
  ggplot2::annotate("text", 
                    # x = rep(max(data$id),3),
                    x =c(0,0,0.2,0.2),
                    y = c(-50, 0, 50, 100),
                    label = c("50","0", "50", "100") , 
                    color="black", 
                    size=5, 
                    angle=0, 
                    # fontface="bold",
                    hjust=1) +
  # Add labels on top of each bar
  geom_text(data=label_data,
            aes(
              x = id,
              y = 101,
              label=individual,
              hjust=hjust),
            color="black",
            # fontface="bold",
            alpha=1,
            size=4,
            angle= label_data$angle,
            inherit.aes = FALSE ) +
  # Continents labels
  geom_text(data=base_data,
            aes(x = title,
                y = 85, 
                label=group), 
            hjust=c(1,1,1,0,0,0),
            colour = "black",
            # alpha=0, 
            size=5,
            fontface="bold",
            inherit.aes = FALSE) +
  ylim(-100,105) +
  theme_minimal() +
  theme(legend.position = c(0.93,0.14),
    legend.key.size = unit(1,"cm"),
    legend.title = element_text(size = 16),
    legend.text = element_text(size = 14),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm")) +
  coord_polar()

@@

ggsave(
    plot = last_plot(),
    width = 17,
    height = 15,
    units = "in",
    # filename = "Plot.png"
    filename = "Territory_circular_status.png",
    path = Figures_Path
  )
